\documentclass[letterpaper,11pt,twocolumn]{article}
\usepackage{usenix,graphicx,times}
%\usepackage{graphics, graphicx, fancyhdr, epsfig, amstext}
%\usepackage{amsmath, amssymb, xspace, setspace, times, color}
\begin{document}
\title{CSCI 373 Project 1: Traffic Jam} 
\date{}
\author{
  {\rm Erik Kessler}\\
       Williams College\\
}

\maketitle

\thispagestyle{empty}
%\pagestyle{empty}
                                   
\begin{abstract}
We describe the 1 paragraph overview of the problem, approach, and experiment results.
\end{abstract}

\section{Introduction}
What is the high-level problem at hand? Why is it worth while developing an AI
agent for this task? (This isn’t such a good question for a toy problem, but it’ll be a good practice
for your final project.)

\section{Formulation}
How did you represent the real-world problem as a search problem (what are valid
states and actions)?

\section{Approaches}
Which algorithms (and heuristics) did use to solve the search problem? Describe at
least 2 distinct approaches and justify your decisions. Your approaches should not depend on the
specifics of the 3 initial states provided to you.

\section{Experiments \& Analysis}
Compare the performances of your approaches with respect to the
number of times the goal-test function was called. Include a table of performance results for each
approach and initial state combination. Reason about the similarities and differences observed.

\section{Conclusion}
Summarize the project (major findings, weaknesses, etc.) and describe an extension
of the project that you’d like to try if you had more time.

\appendix
\section{Solutions}

%\bibliographystyle{plain}
%\bibliography{bibfile}
\end{document}